---
title: "Exploratory data analysis on TCGA Breast Cancer gene expression data"
output: html_notebook
---


Read in the data sets

```{r}
df_exprs <- readRDS("data/TCGA_exprs.rds")
head(df_exprs)

df_clinical <- readRDS("data/TCGA_clinical.rds")
head(df_clinical)

df_pca <- readRDS("data/TCGA_pca.rds")
head(df_pca)
```

# Getting to know the data

### Part 1: Focusing on a particular gene

Do ER+ and ER- patients exhibit differences in the expression of a particular gene of interest (ESR1)?

```{r}
# your code
```

Do PAM50 cancer subtypes exhibit differences in the expression of a particular gene of interest (ESR1)?

```{r}
# your code
```

### Part 2: High-dimensional data (considering all genes)

First, convert the expression data into tidy format

```{r}
# your code
```

Join the three different data sets, using the sample IDs for merging. This will be useful for further analysis. 

```{r}
# your code
```

As a first step, to get an idea of distributions, let's make histograms of expression for some of the genes (e.g. 10 randomly selected genes). 

```{r}
# your code
```

Considering all genes, do ER+ and ER- patients have generally quite different expression profiles, or are they quite similar?

```{r}
# your code
```

Considering all genes, do PAM50 subtypes have generally quite different expression profiles, or are they quite similar? 

```{r}
# your code
```

